\texttt{dfoliatR}: An R package for detection and analysis of insect defoliation signals in tree rings

### 2020-09-02 dfoliatR_ms.tex

\leavevmode\hypertarget{ref-Cook2004}{}%
Cook, E.R., Krusic, P.J., 2004. The North American Drought Atlas. (Lamont- Doherty Earth Observatory; the National Science Foundation: New York) Available at https://www.ncdc.noaa.gov/data-access/paleoclimatology-data/datasets/tree-ring/drought-variability {[}Last accessed May 2020{]}.

>>>>

\leavevmode\hypertarget{ref-Cook2004}{}%
Cook, E.R., Krusic, P.J., 2004. The North American Drought Atlas. (Lamont-Doherty Earth Observatory; the National Science Foundation: New York) Available at https://www.ncdc.noaa.gov/data-access/paleoclimatology-data/datasets/tree-ring/drought-variability {[}Last accessed May 2020{]}.
